## Examples
The `pinbasic` packages is equipped with four synthetic datasets of daily buys and sells, 
`BSinfrequent`, `BSfrequent`, `BSfrequent2015` and `BSheavy`. 
They represent infrequently, frequently and heavily traded equities, respectively. 
The datasets `BSinfrequent`, `BSfrequent` and `BSheavy` cover 60 trading days, whereas 
`BSfrequent2015` contains simulated daily buys and sells for business days in 2015. 
The datasets can be loaded with `data` function.

```{r dataloading}
data("BSinfrequent")
data("BSfrequent")
data("BSfrequent2015")
data("BSheavy")

summary(BSinfrequent)
summary(BSfrequent)
summary(BSfrequent2015)
summary(BSheavy)
```

For estimating the probability of informed trading $\pintext$ `pin_est` function can be utilized. 
Exemplary, $\pintext$ for `BSheavy` dataset is estimated.

```{r pinest, eval = FALSE}
# using default values for lower and upper bounds
# confidence interval computation enabled
pin_bsheavy <- pin_est(numbuys = BSheavy[,"Buys"],
                       numsells = BSheavy[,"Sells"], 
                       confint = TRUE, ci_control = list(n = 1000, seed = 123), 
                       posterior = TRUE)
```

```{r loadpinest, echo = FALSE}
pin_bsheavy <- readRDS("../RDSfiles/pin_bsheavy.rds")
```

```{r strpinheavy}
# structure of returned list
str(pin_bsheavy)

# convert matrix to data.frame for prettier output in the vignette
as.data.frame(pin_bsheavy$Results)
```

If model parameter estimates and therefore estimates of $\pintext$ on a quarterly basis 
are required, `qpin` function which 
takes care of automatic dataset splitting is an appropriate choice.  
The `BSfrequent2015` dataset covers four quarters and a total of `r nrow(BSfrequent2015)` trading days. 
Dates of trading days are stored in its rownames, so they can be passed to the `dates` argument of `qpin`.

```{r qpin}
# dates stored in rownames of dataset
head(rownames(BSfrequent2015))
```

```{r qpin2015, eval = FALSE}
# quarterly PIN estimates
# confidence interval computation enabled:
#   * using only 1000 simulated datasets
#   * confidence level set to 0.9
#   * seed set to 287

qpin2015 <- qpin(numbuys = BSfrequent2015[,"Buys"],
                 numsells = BSfrequent2015[,"Sells"],
                 dates = as.Date(rownames(BSfrequent2015), format = "%Y-%m-%d"),
                 confint = TRUE, ci_control = list(n = 1000, level = 0.9, seed = 287))
```

```{r qpin2015rds, echo = FALSE}
qpin2015 <- readRDS("../RDSfiles/qpin2015.rds")
```

```{r qpin2015sum}
# list of length 4 is returned
names(qpin2015[["res"]])

# confidence intervals for all four quarters
ci_quarters <- lapply(qpin2015[["res"]], function(x) x$confint)
ci_quarters

# each list element has the same structure as results from pin_est function
# convert matrices to data.frames for prettier output in the vignette
qpin2015_res <- lapply(qpin2015[["res"]], function(x) as.data.frame(x$Results))

qpin2015_res[[1]]
qpin2015_res[[4]]
```

Results returned by `qpin` can be visualized with `ggplot`.
```{r}
library(ggplot2)
ggplot(qpin2015[["res"]])
```

Datasets of daily buys and sells can be simulated with `simulateBS` function which offers three arguments. 
Values of model parameters can be set via `param` argument, 
to ensure reproducibility `seed` should be specified and `ndays` determines the number 
of trading which are simulated. 
The probability parameters $\probinfevent$ and $\probbadnews$ are used to sample trading days' conditions. 
Once the sequence of states is computed, number of buys and sells for each trading day are drawn from 
Poisson distributions with intensities according to the scenario tree presented in EHO model section.

We use the estimated parameters of `pin_bsheavy` to simulate data for 100 trading days.

```{r simBS}
# getting the estimates
heavy_est <- pin_bsheavy$Results[,"Estimate"]

# simulate buys and sells data
set.seed(123)
sim_heavy <- simulateBS(param = heavy_est, ndays = 100)

# summary of simulated data
summary(sim_heavy)
```

Computation of confidence intervals for $\pintext$ can either be enabled by `confint` argument of the optimization routines 
(`confint = TRUE` in `pin_est_core`, `pin_est`, `qpin`) or performed with `pin_confint` directly which incorporates `simulateBS` for 
simulation of `n` datasets with the given parameter vector `param`. 
MLE is done for each simulated dataset to receive a total of `n` $\pintext$ estimates.
Quantiles, induced by `level` argument, of this series are calculated by `quantile` function from **stats** package.

We use the simulated `sim_heavy` data together with the corresponding parameter estimates to calculate a confidence interval for the probability 
of informed trading. 
In addition, we compare the execution times of single-core vs. parallel computation.^[
All computations were done on an Intel Core i5-4590 with four physical cores.] 
The higher the number of simulation runs `n` the more the computation benefits from parallel execution.

```{r confint1, eval = FALSE}
# n = 10000 simulation runs, 
# level = 0.95 (confidence level)

system.time(heavy_ci <- pin_confint(param = heavy_est, 
                                    numbuys = sim_heavy[,"Buys"],
                                    numsells = sim_heavy[,"Sells"],
                                    seed = 321, ncores = 1))
```

```{r confintsystime1, echo = FALSE}
systime1 <- readRDS("../RDSfiles/systimeci1.rds")
heavy_ci <- readRDS("../RDSfiles/ci1.rds")
systime1
```

```{r confint4, eval = FALSE}
# same setting but 4 cpu cores
system.time(heavy_ci4 <- pin_confint(param = heavy_est, 
                                     numbuys = sim_heavy[,"Buys"],
                                     numsells = sim_heavy[,"Sells"],
                                     seed = 321, ncores = 4))
```

```{r confintsystime4, echo = FALSE}
systime4 <- readRDS("../RDSfiles/systimeci4.rds")
heavy_ci4 <- readRDS("../RDSfiles/ci4.rds")
systime4
```

```{r compare}
heavy_ci
heavy_ci4
```

Posterior probabilities of trading days' condition are returned by `posterior` and can be displayed with `ggplot`. 
Exemplary, we compute posteriors for `BSheavy` dataset and use corresponding parameter estimates stored in `heavy_est`.

```{r post}
# Calculating posterior probabilities
post_heavy <- posterior(param = heavy_est,
                        numbuys = BSheavy[,"Buys"], numsells = BSheavy[,"Sells"])

# Plotting                        
ggplot(post_heavy)
```

If x axis should show dates, names of `numbuys` and `numsells` need to be either in `"%Y-%m-%d"` or `"%Y/%m/%d"` format which can be converted with `as.Date`. 
The following code chunk shows how posterior probabilities for `BSfrequent2015` in the third quarter can be visualized. 
```{r postdates}
# Corresponding parameter estimates
freq_2015.3 <- qpin2015[["res"]]$'2015.3'$Results[,"Estimate"]

# Subsetting data
third_quarter <- subset(BSfrequent2015, subset = lubridate::quarter(rownames(BSfrequent2015)) == 3)

# Calculating posterior probabilities
post_third <- posterior(param = freq_2015.3, 
                        numbuys = third_quarter[,"Buys"], numsells = third_quarter[,"Sells"])

# Plotting
ggplot(post_third)
```


