### Package Interface

The `pinbasic` package offers the `initial_vals` function for generating set(s) of starting values
which can be used in optimization routines estimating the probability of informed trading.
It is a wrapper around the specialized functions `init_grid_search`, `init_hac` and
`init_hac_ref`.^[
The specialized functions for generating initial values are not exported.]
Arguments `numbuys` and `numsells` take vectors of daily buys and sells.
The algorithm for calculating initial values can be specified via `method` argument
by which the user can choose one of the previous discussed methods.
Brute force grid search algorithm can be chosen via `"Grid"`,
for HAC or refined HAC algorithm `method` needs to equal `"HAC"` or `"HAC_Ref"`.
```{r insert-initial_vals, echo=FALSE, cache = FALSE}
insert_fun('initial_vals')
```{r initial_vals-source, eval=FALSE}
```
In addition, there are method-specific arguments `length`, `num_clust` and `details`.
The `length` argument is relevant for grid search in which
`length` determines the grid width by which the interval $\left[0.1, 0.9\right]$ is splitted.
This influences the amount of possible initial values for the probability parameters \probinfevent\ and \probbadnews\
as well as $\gamma$.
If `details` is set to `TRUE` and `method = "Grid"` a list is returned with elements
representing a matrix with sets of starting values, the number of sets removed due to negative values for the intensity of uninformed sells
and guesses for the intensity of informed trading that are larger than the highest observed number of buys or sells in the data.
Otherwise, solely a matrix of initial values is returned.
For the combination `method = 'HAC_Ref'` and `details = TRUE` a matrix with `num_clust` sets of starting values is returned
including the corresponding likelihood function values.
Hence, `num_clust` determines the number of clusters the trading data is grouped in and is only relevant for `method = "HAC_Ref"`.
The best set of initial values generated by refined HAC method is returned if `details = FALSE`.

