### Package Interface
The package is equipped with the `pin_ll` function.
It computes likelihood functions in the static $\pintext$ models,
either incorporating the factorization by @EHO2010 or @LinKe.
The function is designed for the extended EHO model, but can also be applied to the simple model structure
for equal values of $\intensuninfbuys$ and $\intensuninfsells$.

```{r insert-pin_ll, echo=FALSE, cache = FALSE, include = FALSE}
insert_fun('pin_ll')
```{r pin_ll-source, eval=FALSE}
```

The `pin_ll` function receives trading data via the arguments `numbuys` and `numsells`,
which take numeric vectors of equal length for daily buys and sells.
Model parameters can be passed with `param` argument. % but the length of the vector needs to equal 5 or an
error is thrown to the console and computation is aborted.
For the `factorization` argument the user can choose between `"Lin_Ke"` and `"EHO"` strings.
The numeric vector passed to `param` argument is pre-checked with `param_check` function.
It is verified that the length of the vector equals 5,
otherwise an error is thrown to the console and computation is aborted.
Either `param` has to be a named vector or sorting of entries needs to be done properly.
If names are not set or one or more names do not match the valid choices, `param` is silently renamed with
strings `"alpha"`, `"delta"`, `"epsilon_b"`, `"epsilon_s"` and `"mu"` (in this order).

Function `param_check` as well as
the two specialized functions for computing likelihood function values,
`pin_ll_lin_ke_5par` and `pin_ll_eho_5par`, are not exported.^[
If a user insists on using this functions directly, function calls of the form `pinbasic:::pin_ll_lin_ke_5par` and
`pinbasic:::pin_ll_eho_5par` are sufficient.]